### 2018-08-08 manuscript.rmd
included BAMMtools chunk, incorporates constrained timetree

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(stringr)
library(reshape2)
	## Biological
library(OUwie)
library(Rphylip)
library(arbutus)
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
	## Graphics
library(FactoMineR)
library(factoextra)
library(corrplot)

@@

```{r load_tree, include=F}
#Load tree
#consensus = ape::read.tree("concatenate.fasta.contree")
consensus = read.nexus("gene_map_ct.tre")
read.tree("gene_ct.trees") %>% consensus() -> daconsensus
plot(daconsensus)
#consensus = reroot(consensus,103)
consensus = reroot(consensus,97)
#consensus = drop.tip(consensus, c(28,29,30,59:61))
consensus = drop.tip(consensus, c(56:61))
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
ultra_consensus = chronos(consensus,100)

#PLOT tree figure
plot(ultra_consensus)

@@

ultram = chronos(prunedtree)
plot(ultram)

@@

2.4 Table showing normalized rates of evolution for each character BAMM.
3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing

>>>>

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(stringr)
library(reshape2)
	## Biological
library(OUwie)
library(Rphylip)
library(arbutus)
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
	## Graphics
library(FactoMineR)
library(factoextra)
library(corrplot)
library(BAMMtools)

@@

```{r load_tree, include=F}
#Load tree
#consensus = ape::read.tree("concatenate.fasta.contree")
#consensus = read.nexus("gene_map_ct.tre")
#read.tree("gene_ct.trees") %>% consensus() -> daconsensus
#plot(daconsensus)
consensus = read.nexus("TimeTreeCT.tre") %>% drop.tip(53:58)
#consensus = reroot(consensus,103)
#consensus = reroot(consensus,97)
#consensus = drop.tip(consensus, c(28,29,30,59:61))
#consensus = drop.tip(consensus, c(56:61))
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
#ultra_consensus = chronos(consensus,100)

@@

#ultram = chronos(prunedtree)
ultram = prunedtree
plot(ultram)

@@

2.4 Table showing normalized rates of evolution for each character BAMM.

```{r BAMM}

3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing
